### 2023-07-13 2.State/lstm.tex
finishing lstms
New lstm figures and text
update to lstm, unfinished

>>>>

\subsection{Usage}

Using \ac{LSTM} can be a bit tricky. Due to it's sequential nature, it takes several time steps. Every hidden state ($h_t$) is passed to the next time step as an input. This hidden state can be used to compute an output at any time step $t$.

\begin{figure}[H]
  \centering
  \includesvg[width=\textwidth]{lstm/lstmUse}
  \caption{LSTM Cell}
  \label{fig:lstmCell}
\end{figure}

\subsection{Variants}

\acp{LSTM} come in reality in a few different flavor. Usually, when \acp{LSTN} are mentionned, the version used is the \ac{NP} version. This is the most common version because it gives the best results in most situations.
There are other variants of the \ac{LSTM}, that have slight variations in the equations.
